\documentclass[conference]{IEEEtran}

\usepackage{graphicx}
\usepackage[section]{placeins}
\newcommand{\comment}[1]{}

\begin{document}

\title{Qualitative Cache Performance Analysis}

\author{}
%\author{Andrew Carter \and Max Korbel \and Paula Ning \and Seth Pugsley \and Josef Spjut}

\maketitle

\begin{abstract}
The effectiveness of caching policies has been measured by a number of metrics. 
The ultimate quantitative measure is overall system performance.
Other metrics such as hit rate, misses per thousand instructions and
instructions per cycle are also regularly used in the literature to
compare cache behaviors.
In this work we propose a novel class of metrics based on the idea
that any memory element should ideally be kept out of the cache
for as long as possible before being fetched again, an idea inspired
by Belady's algorithm.
In general we measure the Time to Recache for each evicted element as a qualitative measurement of a caching policy's performance.
Among this set of metrics, we analyze the number of Memory Accesses and Memory Misses to Recache, as well as a rough approximation
of Wall-Time to Recache.
We believe that these metrics will not only be useful for comparing the performance of two different caching policies,
  but allow designers of such policies to identify memory access
  patterns that are problematic for existing policies.
We also provide our simulation and testing methodology and source to
assist others in applying these metrics to their own
studies.
\end{abstract}

\input{tex/01-introduction}
\input{tex/02-motivation}
\input{tex/03-methodology}
\input{tex/04-results}
\input{tex/05-analysis}
\input{tex/06-relatedwork}
\input{tex/07-conclusions}

\bibliographystyle{abbrv}
\bibliography{bib/main}

\end{document}
